



## Libraries

```{r}
library(tidyverse)
library(tabulapdf)
library(paws)
library(googlesheets4)
library(stringr)
```


```{r}

```
## Extraction
```{r}
house_pdf <- file.choose()
house_fy26_extract <- extract_tables(house_pdf, page = 1)


senate_pdf <- file.choose()
senate_fy26_extract <- extract_tables(senate_pdf, page = 1)
```

## Base Table Extraction Code via AWS TextExtract ##
## Takes a pdf from S3, and does (the best it can) to extract into a list of tables ###
```{r}

### SET YOUR AWS CREDENTIALS ### 
textract <- paws::textract()

analyze_document <- function(bucket, file) {
  
  # Start analyzing the PDF.
  resp <- textract$start_document_analysis(
    DocumentLocation = list(
      S3Object = list(Bucket = bucket, Name = file)
    ),
    FeatureTypes = "TABLES"
  )
  
  print(resp)
  
  # Check that the analysis is done and get the result.
  count <- 0
  while (count < 30 && (!exists("result") || result$JobStatus == "IN_PROGRESS")) {
    Sys.sleep(1)
    result <- textract$get_document_analysis(
      JobId = resp$JobId
    ) 
    count <- count + 1
  }
  
  all_blocks <- result$Blocks
  page_count <- 1
  
  # Add a safety counter to prevent infinite loops
  max_pages <- 50  # Adjust based on expected document size
  
  while (!is.null(result$NextToken) && page_count < max_pages) {
    result <- textract$get_document_analysis(
      JobId = resp$JobId,
      NextToken = result$NextToken
    )
    # Use append() instead of c() to properly flatten the list
    all_blocks <- append(all_blocks, result$Blocks)
    page_count <- page_count + 1
    print(paste("Getting page", page_count, "- Total blocks:", length(all_blocks)))
    
    print(all_blocks)
  }
  
  result$Blocks <- all_blocks
  print(results)
  return(result)
}


get_children <- function(block, data) {
  if (length(block$Relationships) == 0) {
    return(list())
  }
  idx <- which(sapply(block$Relationships, function(x) x$Type) == "CHILD")
  if (!idx) {
    return(list())
  }
  child_ids <- block$Relationships[[idx]]$Ids
  result <- data[child_ids]
  return(result)
}

get_tables <- function(analysis) {
  tables <- list()
  print(tables)
  blocks <- analysis$Blocks
  names(blocks) <- sapply(blocks, function(x) x$Id)

  for (block in blocks) {
    
    if (block$BlockType == "TABLE") {
      cells <- get_children(block, blocks)
      rows <- max(sapply(cells, function(x) x$RowIndex))
      cols <- max(sapply(cells, function(x) x$ColumnIndex))
      table <- matrix(nrow = rows, ncol = cols)
      
      # 1. Go through a table's cells one-by-one
      for (cell in cells) {
        
        # 2. Get the cell's contents
        words <- get_children(cell, blocks)
        text <- paste(sapply(words, function(x) x$Text), collapse = " ")
        
        # 3. Insert the cell contents into the matrix
        row <- cell$RowIndex
        col <- cell$ColumnIndex
        table[row, col] <- text
      }
      tables <- c(tables, list(table))
    }
  }
  return(tables)
} 

```


## Procesing Senate through Extract - pushing to googlesheets for hand clean up, and then pulling back in here to save via project folder ##
```{r}
senate_earmarks <- analyze_document("water-team-data", "srf-earmarks/2026-earmarks/fy26_interior_cds.pdf")
tables <- get_tables(senate_earmarks)
senate_tables <- data.frame(tables[[10]])

ss <- "16VSpaRJGbybgRvilsGngF1Rzu3mYTIWM02yZOnV-RdQ"

# Write each table to a separate tab
for (i in seq_along(tables)) {
  sheet_write(as.data.frame(tables[[i]]), 
              ss = ss, 
              sheet = paste0("Table_", i))
  
  
## Fixed issues and assembled by hand here -> https://docs.google.com/spreadsheets/d/16VSpaRJGbybgRvilsGngF1Rzu3mYTIWM02yZOnV-RdQ/edit?gid=0#gid=0
## Downloaded into clean-data folder
  
senate_earmarks_clean <- read_sheet("https://docs.google.com/spreadsheets/d/16VSpaRJGbybgRvilsGngF1Rzu3mYTIWM02yZOnV-RdQ/edit?gid=0#gid=0")

write.csv(senate_earmarks_clean, "clean-data/senate_earmarks_clean_v1.csv")
}

```

## House Earmarks - Processed in Claude and brought in here 
```{r}
# Raw data uploaded to Claude, prompted, cleaned and pasted here -> https://docs.google.com/spreadsheets/d/19oGMbPMJAz0ZAPNChvzX5AHlgaHhZcb4R6CpIS8jLNM/edit?gid=142064248#gid=142064248

house_earmarks_clean <- read_sheet("https://docs.google.com/spreadsheets/d/19oGMbPMJAz0ZAPNChvzX5AHlgaHhZcb4R6CpIS8jLNM/edit?gid=142064248#gid=142064248")

write.csv(house_earmarks_clean, "clean-data/house_earmarks_clean_v1.csv")

```


## Cleaning and Combining for using alongside existing data 
```{r}
house_earmarks_prep <- house_earmarks_clean %>%
                       filter(str_detect(Account, "State Revolving Fund"))%>%
                       rename(House_Requestor = Requestor)%>%
                       mutate(Originiation = "H")%>%
                       mutate(Senate_Requestor = "")%>%
                       mutate(Amount = as.character(Amount))

senate_earmarks_prep <- senate_earmarks_clean %>%
                        filter(str_detect(Account, "State Revolving Fund"))%>%
                        rename(Senate_Requestor = Requestor)%>%
                        mutate(Originiation = "S")%>%
                        mutate(House_Requestor = "")%>%
                       mutate(Amount = str_remove_all(Amount, ","))

# combining and saving 
## QA
earmarks_26 <- bind_rows(senate_earmarks_prep,house_earmarks_prep)

write.csv(earmarks_26, "clean-data/earmarks_26_v1.csv")

```
## Ingesting and Saving Cap Allotments
```{r}
cw_25_cap <- read_sheet( "https://docs.google.com/spreadsheets/d/1o4n-orXTnQer7eDshVghDJwsJ2fgfTuOOwy1IV9zuBM/edit?gid=0#gid=0", "CW_25_cap")%>%
             select(-c(`Total Funds`))

write.csv(cw_25_cap, "clean-data/cw_25_cap_v1.csv", row.names = FALSE)

dw_25_cap <- read_sheet( "https://docs.google.com/spreadsheets/d/1o4n-orXTnQer7eDshVghDJwsJ2fgfTuOOwy1IV9zuBM/edit?gid=0#gid=0", "DW_25_cap")

write.csv(dw_25_cap, "clean-data/dw_25_cap_v1.csv", row.names = FALSE)


```

## 2025 Earmarks Placeholder (there were no earmarks for 2025 but we need an empty dataframe)
```{r}
earmarks_25 <- earmarks_26 %>%
               filter(is.na(State))

write.csv(earmarks_25, "clean-data/earmarks_25_v1.csv")
  
```


## Creating 2026 cap based off 2025
## we take the 2025 cap - less the earmarks to get us 2026 numbers
```{r}

## Drinking Water
## Total 2025 allotment - 2026 earmarks * state allocation % = state allocations 
dw_cds_2026_total <- earmarks_26 %>%
                    filter(str_detect(Account,"Drinking")) %>% 
                    group_by(Account) %>%
                    summarise(Amount = sum(as.numeric(Amount), na.rm = TRUE))%>%
                    pull(Amount)

dw_allot_2026_total <- 1090579000 - dw_cds_2026_total # 2025 total allotment - 2026 earmarks 

dw_26_cap <- dw_25_cap %>%
             select(state, pct)%>%
             mutate(allotment = pct * dw_allot_2026_total)

write.csv(dw_26_cap, "clean-data/dw_26_cap_v1.csv", row.names = FALSE)


## Clean Water
## Total 2025 allotment - 2026 earmarks * state allocation % = state allocations 
cw_cds_2026_total <- earmarks_26 %>%
                    filter(str_detect(Account,"Clean")) %>% 
                    group_by(Account) %>%
                    summarise(Amount = sum(as.numeric(Amount), na.rm = TRUE))%>%
                    pull(Amount)

cw_allot_2026_total <- 1602584000 - dw_cds_2026_total  # 2025 total allotment - 2026 earmarks 

cw_26_cap <- cw_25_cap %>%
             select(state, pct)%>%
             mutate(allotment = pct * cw_allot_2026_total)

write.csv(cw_26_cap, "clean-data/cw_26_cap_v1.csv", row.names = FALSE)




```



